Stabilization-Free Virtual Element Methods

### 2022-06-12 stabfreevem.tex
update

\section{Numerical examples}\label{sec:numericalexamps}

>>>>

\begin{figure}[htbp]
\centering
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=5cm]{./figures/convex.pdf}
%\caption{Numberical result of example with $\mathcal T_0$.}
\end{minipage}%
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=5cm]{./figures/nonconvex.pdf}
%\caption{[Numberical result of example with $\mathcal T_1$].}
\end{minipage}%
\centering
\caption{Convex polygon mesh $\mathcal T_0$(left) and non-convex polygon mesh 
$\mathcal T_1$(right).}
\label{fig:mesh}
\end{figure}

\section{Numerical examples}\label{sec:numericalexamps}
In this section, we solve \eqref{eq:ellipitc2ndproblem} using the conforming
virtual element method and the nonconforming virtual element method, 
and give numerical results to verify convergence rates.

\begin{example}\label{ex}
    Consider the second order elliptic problem \eqref{eq:ellipitc2ndproblem}
    on rectangular domain $\Omega = (0, 1)\times(0, 1)$, take $\alpha = 2$, 
    the exact solution and source term are:
    $$
    u = \sin(\pi x)\sin(\pi y), \quad f = (2\pi^2+2)\sin(\pi x)\sin(\pi y)
    $$
\end{example}

The rectangular domain $\Omega$ is partitioned by the convex polygon mesh
$\mathcal T_0$ and non-convex polygon mesh $\mathcal T_1$, respectively, 
as shown in Figure \ref{fig:mesh}. The numerical results for $k = 1, 2, 5$ are 
listed in Figure \ref{fig:ncvemrate} \ref{fig:cvemrate}, 
where the errors use $L^2$ norm and $H^1$-like norm. Both cases confirm the
theoretic convergence rates.

\begin{figure}[htbp]
\centering
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=6cm]{./figures/ncvemrate_convex.png}
%\caption{Numberical result of example with $\mathcal T_0$.}
\end{minipage}%
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=6cm]{./figures/ncvemrate_noconvex.png}
%\caption{[Numberical result of example with $\mathcal T_1$].}
\end{minipage}%
\centering
\caption{Error $\|u - Q_h u_h\|_0$ and $\|\nabla u - Q_{h, k-1}^{div}\nabla u_h\|_0$ 
of Example \ref{ex} on $\mathcal T_0$(left) and $\mathcal T_1$(right) with $k=1, 2, 5$.}
\label{fig:ncvemrate}
\end{figure}

\begin{figure}[htbp]
\centering
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=6cm]{./figures/cvemrate_convex.png}
%\caption{Numberical result of example with $\mathcal T_0$.}
\end{minipage}%
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=6cm]{./figures/cvemrate_noconvex.png}
%\caption{[Numberical result of example with $\mathcal T_1$].}
\end{minipage}%
\centering
\caption{Error $\|u - Q_h u_h\|_0$ and $\|\nabla u - Q_{h, k-1}^{div}\nabla u_h\|_0$ 
of Example \ref{ex} on $\mathcal T_0$(left) and $\mathcal T_1$(right) with $k=1, 2, 5$.}
\label{fig:cvemrate}
\end{figure}
